%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
  {Senior Backend Engineer (Freelance)}
  {Back Market — Marketplace / Fintech}
  {Paris, France — Remote}
  {March 2026 -- Present}
  {
    \begin{cvitems}
      \item {Worked on event-driven integrations (Pub/Sub) to ingest and register financial transactions into a microservice-based ledger system.}
      \item {Contributed to the invoicing system re-architecture, including provider integrations and the evolution of financial workflows.}
      \item {Added observability (metrics, alerts) to financial data pipelines in production, following established monitoring practices.}
      \item {Contributed to architectural improvements around event versioning and schema evolution, including writing ADRs and proposing changes for long-term maintainability.}
      \item {Worked on backend services (\textbf{Python}, \textbf{FastAPI}, Pydantic, SQLAlchemy) within a microservices architecture handling financial domains such as invoicing and accounting.}
      \item {Started developing an internal CLI tool in \textbf{Go} to monitor and debug Pub/Sub event flows related to financial transactions.}
      \item {Mentored junior engineer on software design patterns, code structure, and testing practices.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Engineering Manager (Hands-on)}
  {NALA — Fintech}
  {London, UK — Remote}
  {Sept 2025 -- Nov 2025}
  {
    \begin{cvitems}
      \item {Led delivery of pricing system improvements for financial products, reducing reliance on manual price adjustments and enabling faster iteration on pricing logic.}
      \item {Designed and implemented automation mechanisms for pricing adjustments based on market signals, improving responsiveness while keeping operational control.}
      \item {Introduced safeguards and validation layers to improve pricing consistency and reduce risk in automated workflows.}
      \item {Implemented backend changes in \textbf{Golang} and AWS, including support for reverse currency flows (LCY $\rightarrow$ HCY).}
      \item {Worked closely with product to prioritize and deliver incremental improvements across the pricing domain.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {CTO (Hands-on) / Principal Engineer}
  {ZYTLYN — Data Intelligence}
  {Geneva, Switzerland — Remote}
  {July 2021 -- Sept 2025}
  {
    \begin{cvitems}
      \item {Designed and built the company’s core data platform from scratch, implementing batch-first ETL pipelines (Python, Spark, Kafka) to ingest, transform, and unify heterogeneous datasets into a scalable data lake.}
      \item {Architected the S3-based data lake and transformation layer powering analytics workloads, with pipelines designed for schema evolution and new source onboarding.}
      \item {Built and maintained internal and customer-facing APIs (\textbf{FastAPI}, PostgreSQL, DynamoDB) to expose platform capabilities and data products.}
      \item {Implemented the initial ML pipeline infrastructure to support model training and data-driven insights delivery.}
      \item {Defined and implemented cloud infrastructure on AWS (\textbf{EKS}, \textbf{Terraform}, Docker), including CI/CD pipelines and observability with Prometheus and Grafana.}
      \item {Led a fully remote engineering team of 4 while remaining actively involved in system design, implementation, and code reviews.}
    \end{cvitems}
  }
%---------------------------------------------------------
\cventry
  {Lead Data Engineer} % Job title
  {Bloom - Data Intelligence} % Organization
  {Paris, France - Remote} % Location
  {July 2020 – July 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Led the design and development of a real-time data streaming pipeline using \textbf{Kubernetes, Kafka, gRPC, and Golang} (Goka and Sarama), focused on long-term scalability and maintainability.}
      \item {Led the architectural transition from a PostgreSQL-based monolith to a distributed \textbf{microservices system}, balancing legacy support with forward-looking design.}
      \item {Developed both stateful and stateless services to handle job state, tokenization, and data transformation with reliability and performance in mind.}
      \item {Mentored engineers on Golang best practices and Kafka streaming patterns, helping grow internal expertise and autonomy within the team.}
      \item {Conducted R\&D using Spark GraphX to explore new approaches to social graph processing and influence modeling.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {PredictHq - Data Intelligence} % Organization
    {Auckland, New Zealand - Remote} % Location
    {January 2017 – July 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed Python-based microservices to support a real-time event intelligence platform (20M events a day), leveraging \textbf{Kafka, Elasticsearch, and Kubernetes} for scalable data processing across global event feeds.}
        \item {Built ingestion pipelines for diverse data sources including public datasets, paid APIs, batch deliveries, and web scraping — handling data enrichment, normalization, deduplication, and augmentation workflows.}
        \item {Collaborated with the Lead SRE and the Solution Architect to continuously optimize system \textbf{performance, scalability, and architecture}, improving processing reliability as data volumes grew.}
        \item {Supported sales teams with technical expertise during partner and client meetings across Europe, providing architecture explanations and integration guidance.}
        \item {Improved CI/CD pipelines and microservice modularization using \textbf{Helm, Kubernetes, and GitLab CI/CD} to streamline deployments and maintainability.}
        \item {Reviewed service architecture, code structure, and engineering practices to improve consistency and code quality across the team.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Payplug - Fintech Startup} % Organization
    {Paris, France} % Location
    {November 2015 – June 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Python microservices for PayPlug's payment processing platform, focusing on customer account management and payment flows.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Makazi - Data Management Platform} % Organization
    {Paris, France} % Location
    {August 2015 – November 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented distributed data pipelines using Scala, Akka, and Kafka for a new data management platform.}
        \item {Trained and mentored the engineering team in functional programming, CQRS, event sourcing, and reactive architecture principles.}
        \item {Conducted R\&D using Apache Spark to investigate production issues, data consistency, and large-scale data processing challenges.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Smartjog Ymagis Logistics - DCP Delivery Platform} % Organization
    {Montrouge, France} % Location
    {July 2014 – July 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Scala and Akka-based transfer platform for managing digital cinema package (DCP) multicast satellite delivery systems.}
        \item {Enhanced Python modules for platform supervision, transfer management, and delivery queue coordination.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Developer} % Job title
    {Arkena - Content Delivery System} % Organization
    {Ivry sur Seine, France} % Location
    {May 2009 - December 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led the modernization of Java-based content delivery systems, migrating toward multi-tier architecture with Spring, Hibernate, Tomcat clusters, and developing SOAP web services using Axis2 for platform integration.}
        \item {Designed and implemented a workflow system (Step Functions / Airflow-like) to handle content management processes based on Hazelcast and MongoDB.}
        \item {Developed Python-based deployment, configuration, and supervision tools.}
        \item {Designed distributed workflows for transcoding and content management using OpenStack Swift, Celery, Flask and FFMPEG.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
